6.867 Problem Set 3

### 2015-11-11 HW3/tex/HW3.tex
[hw3] boo.

When training

>>>>

When training on the MNIST data, we capped the number of iterations of our gradient descent (for both full batch and SGD) so that to convergence wouldn't take forever. Furthermore, in practice, this may serves as a way of preventing overfitting as long as we are still getting reasonably close.

Again, we observe that full gradient descent performs better than SGD. However, in this case, we see the performance difference to be much more substantial than what we saw in the toy data. This is mostly the result of the 5000 iteration cap we imposed on the gradient descent procedure. Since we often hit the cap in our training, full-batch was considerably closer to convergence compared to the SGD case as the each full-batch update more reliably and steadily minimizes the loss. Again, however each SGD update was considerably faster than a full-batch update. If we allowed the SGD to continue a little longer, we probably the results from our SGD probably would've considerably closer to the full-batch case.
